---
output:
  md_document:
    variant: markdown_github
---

# modelr

<!--
[![Travis-CI Build Status](https://travis-ci.org/hadley/modelr.svg?branch=master)](https://travis-ci.org/hadley/modelr)
[![Coverage Status](https://img.shields.io/codecov/c/github/hadley/modelr/master.svg)](https://codecov.io/github/hadley/modelr?branch=master)
-->

The goal of the modelr package is to provide functions that help you create elegant pipelines when modelling. The package design follows Hadley Wickham's [tidy tool manifesto](https://mran.microsoft.com/web/packages/tidyverse/vignettes/manifesto.html).

## Installation and Documentation

You can install modelr from github with:

```
# install.packages("devtools")
devtools::install_github("hadley/modelr")
```

Alternatively, modelr is available as part of [the tidyverse package](http://blog.revolutionanalytics.com/2016/09/tidyverse.html) which can be installed via:

```
install.packages("tidyverse")
```

Note that unlike the core tidyverse packages, modelr would not be loaded via `library(tidyverse)`. Instead, you can load it explicitly:

```{r}
library(modelr)
```

Full documentation is available in [R for Data Science](http://r4ds.had.co.nz/), especially in the [Model basics](http://r4ds.had.co.nz/model-basics.html) chapter.

## Main Features

### Partitioning and sampling

The `resample` class stores a "pointer" to the original dataset and a vector of row indices. `resample` can be turned into a dataframe by calling `as.data.frame`. The indices can be extracted using `as.integer`:

```{r}
# a subsample of the first ten rows in the data frame
rs <- resample(mtcars, 1:10)
as.data.frame(rs)
as.integer(rs)
```

The class can be utilized in generating an exclusive partitioning of a data frame:

```{r}
# generate a 30% testing partition and a 70% training partition
ex <- resample_partition(mtcars, c(test = 0.3, train = 0.7))
lapply(ex, dim)
```

modelr offers several resampling methods that result in a list of `resample` objects (organized in a data frame):

```{r}
# bootstrap
boot <- bootstrap(mtcars, 100)
# k-fold cross-validation
cv1 <- crossv_kfold(mtcars, 5)
# Monte Carlo cross-validation
cv2 <- crossv_mc(mtcars, 100)

dim(boot$strap[[1]])
dim(cv1$train[[1]])
dim(cv1$test[[1]])
dim(cv2$train[[1]])
dim(cv2$test[[1]])
```

